Proposed Solution

### 2016-11-14 Ennan-Proposal/agenda.tex
stuff

The proposed project is supposed to last three years. We have identified three main 
goals of the project, each of them taking approximately a year:
\begin{description}
\item[Language Model] 
Our language model has to be expressive enough to be able to express and detect 
many non-trivial misconfiguration cases.
We will, therefore, need to define a more comprehensive language model (than the one presented).  The configuration files of some of software systems, 
\eg, squid, are not limited to the keyword-value parameters; thus,
we need to extend the current language model.
\item [Learning Algorithms]
We outlined basic learning algorithms. However, those are just outlines and
many details are left unspecified.
As we pointed out, especially in the 
probabilistic learner case finding the right thresholds will be one of the main tasks.
We plan to investigate some existing learning algorithms for programs, \eg,
Raychev {\em et al.}~\cite{raychev15predicting, raychev16learning}. 
However, the configuration files have a specific structure and directly applying 
existing rules will not be possible. We will try to adapt some of these algorithms 
to our problem.
\item [Real-Wolrd Evaluation]
Finally, we will implement and evaluate \app on real world misconfigurations.
In addition to evaluating \app on TravisCI files, during the development process 
we will empirically  evaluate efficiency, usability, and
accuracy of \app. We plan to use the existing publicly available dataset of 
misconfigurations~\cite{configdataset}. The set is large enough to use some parts as a  training data and some parts for evaluation.
\end{description}

>>>>

The proposed project is supposed to last three years. We have identified three main 
goals of the project, each of them taking approximately a year:
\begin{description}
\item[Language Model] 
Our language model has to be expressive enough to be able to express and detect 
many non-trivial misconfiguration cases.
We will, therefore, need to define a more comprehensive language model (than the one presented).  The configuration files of some of software systems, 
\eg, squid, are not limited to the keyword-value parameters; thus,
we need to extend the current language model.
\item [Learning Algorithms]
We outlined basic learning algorithms. However,
many details are left unspecified and finding the right thresholds will be one of the main tasks.
We plan to investigate some existing learning algorithms for programs, \eg,
Raychev {\em et al.}~\cite{raychev15predicting, raychev16learning}. 
The configuration files have a specific structure and directly applying 
existing rules will not be possible. Still we will try to adapt some of these 
algorithms and ideas
to our problem.
\item [Real-Wolrd Evaluation]
Finally, we will implement and evaluate \app on real world misconfigurations.
In addition to evaluating \app on TravisCI files, during the development process 
we will empirically  evaluate efficiency, usability, and
accuracy of \app. We plan to use the existing publicly available dataset of 
misconfigurations~\cite{configdataset}. The set is large enough to use some parts as a  training data and some parts for evaluation.
\end{description}

### 2016-11-14 Ennan-Proposal/impact.tex
stuff

\item {\bf Complementing post-failure error diagnosis efforts.}
  There is a number of diagnosis and troubleshooting efforts to localize
  the root causes of configuration errors after system failures occur.
  \app's approach of pre-failure error checking
  can be seen as a preliminary checking before installing a
  system. Because \app cab detect many non-trivial
  configuration errors, it simplifies work for
  post-failure error diagnosis tools. Additionally, the output results
  of \app can be used as a guidance for post-failure
  error diagnosis approaches, making them more efficient.

\item {\bf Benefiting other communities, \eg, network misconfiguration.} 
  Besides software misconfiguration, network community has the same 
  misconfiguration problems. In particular, many recent service outage 
  reports exposed network-level configuration error will lead to
  very critical service outages. \app could be extended to reason about
  network-level configuration errors.

>>>>

\item {\bf Complementing post-failure error diagnosis efforts.}
  There is a number of diagnosis and troubleshooting efforts to localize
  the root causes of configuration errors after system failures occur.
  \app's approach of pre-failure error checking
  can be seen as a preliminary checking before installing a
  system. Because \app can detect many non-trivial
  configuration errors, it simplifies work for
  post-failure error diagnosis tools. Additionally, the output results
  of \app can be used as a guidance for post-failure
  error diagnosis approaches, making them more efficient.

\item {\bf Benefiting other communities, \eg, network misconfiguration.} 
  Besides software misconfiguration, network community has the same 
  misconfiguration problems. The ideas presented here could be extended to reason about
  network-level configuration errors.

### 2016-11-14 Ennan-Proposal/intro.tex
stuff

\section*{\app: Automated Verification of Configuration Files}
\paragraph{Overview:} 
Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
We cannot simply apply techniques that exist for software verification: configuration files mainly consists of sequences of assigning some values to system variables.
Additionally, there is no formal specification describing properties of configuration files.

We propose a framework for automated verification of configuration files. We first automatically derive a specification, and the we check if a given configuration 
file adheres to that specification.
The main idea is to analyze a large number of configuration files from publicly available datasets and derive a corresponding specification. To do that we first develop a language model for configuration files. One question we 
need to address is what if there is an error in the given training set. Our proposed framework 
is general enough that it can still derive a correct specification, under 
the assumption that the same error does not appear in a significant amount of files.

@@

\paragraph{Broader Impact:} 
Because configuration files are untyped, unstructured, and mostly undocumented, we are not directly leverage existing techniques for verification as used in programming languages.
Making progress towards verification in such environments, will open the door for work in other domain which have previously been to noisy to handle with existing techniques.
It would complement existing post-failure error diagnosis efforts, and could benefit other verification domains, such as network traffic verification. 
This could significantly reduce large scale system failures without adding any additional burden to users and system developers.

>>>>

\section*{\app: Automated Verification of Configuration Files}
\paragraph{Overview:} 
Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.

We propose a framework for automated verification of configuration files. 
Verifying configuration files is different than verifying standard programs: configuration
files are missing a program structure, but also a specification. They are written in a
very low level programming paradigm: they mainly consists of sequences of assignments 
of some 
values to system variables. In such framework, writing a specification is complex task, 
since it is not clear how should the specification look like and which properties should 
it address. Our framework works as follows: in the pre-processing stage, 
we first automatically derive a specification. Once we have a specification, 
we check if a given configuration 
file adheres to that specification.
The idea about deriving a specification is to analyze a large number of configuration files from publicly available 
datasets and recognize patterns and keyword correlations. We derive from those findings 
a corresponding specification. To do that we first develop a language model for configuration files. One question we 
need to address is: what if there is an error in the given training set? Our proposed framework 
is general enough that it can still derive a correct specification, under 
the assumption that the same error does not appear in a significant amount of files.
We plan to evaluate our framework on real-world configuration files 
used in the TravisIC tool.

@@

\paragraph{Broader Impact:} 
Our main goal is to help to reduce large scale system failures without adding any additional burden to users and system developers. 
Making progress towards verification of configuration files, will enable a static analysis of configuration files. This way potentially disastrous errors can be 
detected before they appear.
We envision \app to complement already existing post-failure error diagnosis efforts.
In addition, this work will also benefit other verification domains, such as network traffic verification.

### 2016-11-14 Ennan-Proposal/prior.tex
stuff

\section{Prior Results from the NSF Support}

The PI received NSF CAREER Award for synthesis in live programming environment
(CCF-1553168 ). In addition, the PI was the publicity chair or the organizer of various
conferences and summer school and she received three grants to support students' visit 
to those venues. The most relevant NSF support for this proposal is the
NSF award ``SHF: Medium: Collaborative Research: FRP for Real'',
(CCF-1302327); \$866,000 (10/01/13-09/30/17), which the PI overtook  from 
Paul Hudak, due to his untimely death. Intellectual Merit: The
proposed work will contribute to a better understanding of declarative models
of time and interaction. Broader Impacts: The proposed work will further broaden
the applicability of FRP, improving implementation making FRP more suitable for
compute-intensive applications, such as interactive 3D graphics and real-time audio
processing. As the part of that grant we also developed and published ConfigC
(acknowledgments to the grant were given). Publications: M. Santolucito, 
E. Zhai, R. Piskac: ``Probabilistic Automated Language Learning for Configuration Files''
(July 2016), CAV 2016, Pages 80-87, DOI: 10.1007/978-3-319-41540-6\_5.

>>>>

\section{Prior Results from NSF Support}

The PI received NSF CAREER Award for synthesis in live programming environment
(CCF-1553168 ). In addition, the PI received some student travel grants to support students' visit 
to conferences or summer schools. The most relevant NSF support for this proposal is the
NSF award ``SHF: Medium: Collaborative Research: FRP for Real'',
(CCF-1302327); \$866,000 (10/01/13-09/30/17), which the PI overtook  from 
Paul Hudak, due to his untimely death. Intellectual Merit: The
proposed work will contribute to a better understanding of declarative models
of time and interaction. Broader Impacts: The proposed work will further broaden
the applicability of FRP, improving implementation making FRP more suitable for
compute-intensive applications, such as interactive 3D graphics and real-time audio
processing. As the part of that grant we also developed and published ConfigC
(acknowledgments to the grant were given). Publications: M. Santolucito, 
E. Zhai, R. Piskac: ``Probabilistic Automated Language Learning for Configuration Files''
(July 2016), CAV 2016, Pages 80-87, DOI: 10.1007/978-3-319-41540-6\_5.
